Scalar_M1

### 2015-05-20 models/Model_Playspace.Rmd
quick look at tuning alpha - find best.alpha by data with highest correlation with human judgemets

```{r}
md <- data %>%
  do(run.rsa(., alpha = 10, useprior = FALSE, usenone = TRUE))

qplot(stars, listener.p, col=degree, 
      data = md, main="Model vs Human judgments") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 2)
```

>>>>

```{r}
md <- data %>%
  do(run.rsa(., alpha = best.alpha, useprior = FALSE, usenone = TRUE))

qplot(stars, listener.p, col=degree, 
      data = md, main="Model vs Human judgments") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 2)

#Which alpha has tightest correlation with human judgements
alphas = seq(from=1, to=25)
cors = sapply(alphas, FUN=function(n) {
  md <- data %>%
    do(run.rsa(., alpha = n, useprior = FALSE, usenone = TRUE))
  cor(md$pred, md$listener.p)
})
qplot(alphas, cors)
best.alpha = which(cors == max(cors))
```
